Parsing Postfix log files

### 2009-04-03 doc/logparser-background.tex
Added a table showing mean and stddev for the number of invocations of each action, for different groups of log files.

    \begin{tabular}[]{ll}

        request                 & smtpd\_access\_policy     \\
        protocol\_state         & RCPT                      \\
        protocol\_name          & SMTP                      \\
        helo\_name              & some.domain.tld           \\
        queue\_id               & 8045F2AB23                \\
        sender                  & foo@bar.tld               \\
        recipient               & bar@foo.tld               \\
        recipient\_count        & 0                         \\
        client\_address         & 1.2.3.4                   \\
        client\_name            & another.domain.tld        \\
        reverse\_client\_name   & another.domain.tld        \\
        instance                & 123.456.7                 \\

    \end{tabular}

>>>>

    \begin{tabular}[]{ll}
        \tabletopline{}%
        Attribute name          & Attribute value           \\
        \tablemiddleline{}%
        request                 & smtpd\_access\_policy     \\
        protocol\_state         & RCPT                      \\
        protocol\_name          & SMTP                      \\
        helo\_name              & some.domain.tld           \\
        queue\_id               & 8045F2AB23                \\
        sender                  & foo@bar.tld               \\
        recipient               & bar@foo.tld               \\
        recipient\_count        & 0                         \\
        client\_address         & 1.2.3.4                   \\
        client\_name            & another.domain.tld        \\
        reverse\_client\_name   & another.domain.tld        \\
        instance                & 123.456.7                 \\
        \tablebottomline{}%
    \end{tabular}

### 2009-04-03 doc/logparser-implementation.tex
Added a table showing mean and stddev for the number of invocations of each action, for different groups of log files.

@@

@@

    \caption{Example of a rule used by \parsernameshort{}}
    \empty{}\label{Example rule in implementation table}
    \begin{tabular}{ll}

    \textbf{Field}      & \textbf{Value}                                    \\
    name                & Unknown sender domain                             \\
    description         & We do not accept mail from unknown domains        \\
    restriction\_name   & reject\_unknown\_sender\_domain                   \\
    program             & \daemon{smtpd}                                    \\
    regex               & \verb!^__RESTRICTION_START__ <(__SENDER__)>: !    \\
                        & \verb!Sender address rejected: Domain not found;! \\
                        & \verb!from=<\k<sender>> to=<(__RECIPIENT__)> !    \\
                        & \verb!proto=E?SMTP helo=<(__HELO__)>$!            \\
    result\_data        &                                                   \\
    connection\_data    &                                                   \\
    action              & \action{DELIVERY\_REJECTED}                       \\
    hits                & 0                                                 \\
    hits\_total         & 0                                                 \\
    priority            & 0                                                 \\
    debug               & 0                                                 \\
    %cluster\_group      & 400                                               \\

    \end{tabular}

>>>>

XXX WRITE ABOUT THE TABLE\@.

@@

\newlength{\tabcolsepORIG}
\setlength{\tabcolsepORIG}{\tabcolsep}
\addtolength{\tabcolsep}{-1pt}

\showtable{build/include-per-file-action-invocation-numbers-table}{Mean and
standard deviation of the number of invocations of each action, for
different groups of log files}{Mean and standard deviation of the number of
invocations of each action, for different groups of log files}

\setlength{\tabcolsep}{\tabcolsepORIG}

@@

    \caption{Example of a rule used by \parsernameshort{}}
    \empty{}\label{Example rule in implementation table}
    \begin{tabular}{ll}
        \tabletopline{}%
        \textbf{Field}      & \textbf{Value}                                    \\
        \tablemiddleline{}%
        name                & Unknown sender domain                             \\
        description         & We do not accept mail from unknown domains        \\
        restriction\_name   & reject\_unknown\_sender\_domain                   \\
        program             & \daemon{smtpd}                                    \\
        regex               & \verb!^__RESTRICTION_START__ <(__SENDER__)>: !    \\
                            & \verb!Sender address rejected: Domain not found;! \\
                            & \verb!from=<\k<sender>> to=<(__RECIPIENT__)> !    \\
                            & \verb!proto=E?SMTP helo=<(__HELO__)>$!            \\
        result\_data        &                                                   \\
        connection\_data    &                                                   \\
        action              & \action{DELIVERY\_REJECTED}                       \\
        hits                & 0                                                 \\
        hits\_total         & 0                                                 \\
        priority            & 0                                                 \\
        debug               & 0                                                 \\
        %cluster\_group      & 400                                               \\
        \tablebottomline{}%
    \end{tabular}
